Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-02-18 energy-planning.tex
implementing Ulrik's comments

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). 
  On the bottom-left it shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan, whereas on the bottom-right the spectrum analysis showing the periodicity of the data exploited in the overall energy model.
  %Follow the collected energy data of a physical aerial robot flying the static coverage.
  }
  \label{fig:il-abs}
  \vspace*{-2ex}
\end{figure}

@@

For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ then indicates it is positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are %the sets of 
integers and reals.% respectively.

The notation $[\,\cdot\,]$ denotes positive naturals up to $\cdot$\,, i.e., $\{0,1,\dots,\,\cdot\,\}$, $\,\cdot\,'$ the transpose of $\cdot\,$, and $[\underline{\,\cdot\,},\overline{\,\cdot\,}]$ the upper/lower bounds of a parameter $\cdot\,$, i.e.,
\begin{equation}
  \underline{\,\cdot\,}\leq\,\cdot\,\leq\overline{\,\cdot\,}.
\end{equation}

@@

\begin{defn}[Triggering and final points]
  \label{def:trigs}
  The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ allows the transition between stages. The \emph{final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
\end{defn}

@@

\begin{defn}[Plan]\label{def:plan}
  The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
    \Gamma_{i+j} & \exists j\in\mathbb{Z},\text{ if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i\\
    \Gamma_i & \text{otherwise}
  \end{cases}.\end{equation*}
\end{defn}

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of an imaginary circle over $\mathbf{p}_{\Gamma_i}$.

Fig.~\ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$, the starting stage, and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$. %The constraint set $\mathcal{C}_{4,1}$ forms the area where 
It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$; the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

\begin{defn}[Primitive stages]
  \label{def:primitive}
  Given the number of \emph{primitive stages} $n\in\mathbb{Z}_{>0}$, a \emph{shift} $\mathbf{d}\in\mathbb{R}^2$, and a final point $\mathbf{p}_{\Gamma_l}$, the stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ %with the path functions $\varphi_1,\dots\varphi_n$ and the parameters $c_1,c_2,\dots,c_n$ 
  are primitive if they form the remainder of the plan with $\mathbf{d}$ up to $\mathbf{p}_{\Gamma_l}$. 
\end{defn}

In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
\begin{equation}\label{eq:primitive}\begin{split}
  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
\end{split}\end{equation}
holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$. $e_j\in\mathbb{R}$ given a shift $\mathbf{d}$, initial point $\mathbf{p}$, and initial value of path parameters $c_1^\rho$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot, e.g., awaits the starting command.

@@

\begin{pb}[Coverage and re-planning-scheduling problem]
  \label{pb:cov-pb}
  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each %vertex $v_i:=(x_{v_i},y_{v_i})%,\forall i\in[|v|]_{>0}$
  %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
  is a point w.r.t. $\mathcal{O}_W$. 
  Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} the optimal parameters $c_i$ in time.
\end{pb}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants. To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies and battery evolution.

@@

Collected energy data and spectrum analysis in Fig.~\ref{fig:il-abs} illustrate the energy of a static coverage plan. %$\Gamma$ with four primitive path functions iterated with a shift. 
Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibit periodic behavior with a constant set of frequencies, independent of the shift. The hypothesis is further backed by the power spectrum analysis, indicating that to model the energy, three frequencies are adequate.

@@

An intuitive way of modeling the energy data is thus a Fourier series of a given order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{R}_{>0}$
\begin{equation}\label{eq:fourier}
  h(t)=a_0/T+(2/T)\sum_{j=1}^{r}{\left(a_j\cos{\omega jt}+b_j\sin{\omega jt}\right)},
\end{equation}
where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the series coefficients.

@@

Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, including regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters. This section summarizes an energy model from our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).

@@

The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average or overall. Additionally, the \powprof{} tool supports the battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}. The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. The measuring device in both $\mathbf{g}$ and $g$ is implicit.

@@

The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
\begin{equation}\label{eq:batdyn}
  \dot{b}(y(t))=-k_bI(y(t))/Q_c,
\end{equation}
where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour. $k_b$ is a battery coefficient added to~\cite{hasan2018exogenous,zhang2018online} and derived experimentally. The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohm, representing the battery resistance. The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts. The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on SoC~\cite{hasan2018exogenous}.

@@

This section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.

@@

There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). These that ensure the completeness %of the cover 
are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.

@@

To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
\begin{equation}\label{eq:r2}
  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
\end{equation}
and is expressed in the function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages. $r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}). The center also changes
\begin{equation}\label{eq:second-circ-gene}
  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
\end{equation}
where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$. Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP. The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$).% in Definition~\ref{def:primitive}).

@@

\begin{figure*}
  \centering
  \begin{subfigure}{.4\textwidth}
    \centering
    \footnotesize
    \input{\figpath/results/new_physics2/trajs3.tikz}
    \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
    \label{fig:trajs}
  \end{subfigure}\hspace*{3ex}
  \begin{subfigure}{.54\textwidth}
    \centering
    \footnotesize
    \input{\figpath/results/new_physics2/ener3.tikz}
    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$), and parameters ($T,b_0$) evolutions}
    \label{fig:ener}
  \end{subfigure}
  \footnotesize
  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}): wind speed and direction, battery behavior, and parameters initial values.}
  \label{fig:res}
\end{figure*}

\vspace*{-1.2ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Simulations} %
\label{sec:experimental}        %
                                %
%$\subsection{Experimental setup}

Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), complement physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}, and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware.
The computing hardware caries a camera as a peripheral and is evaluated independently of the aerial robot with the \powprof{} (see Section~\ref{sec:mod-com}). The scheduler, implemented through Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames-per-second (FPS). The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented through ROS. The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}). The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.

%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
Fig.~\ref{fig:il-abs} details the data of the physical flight  
%We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
in standard atmospheric conditions. 
Fig.~\ref{fig:res} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling in the letter.

@@

\vspace*{-1.2ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Directions}  %
\label{sec:conclusion}                       %
                                             %
This letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature. It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings. Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool. The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC. It evolves the state of the energy model while optimizing battery usage and remedying possible defects. The plan compromise multiple stages, where at each the aerial robot flies a path and runs the computations, allowing further extensibility in terms of constructs and approaches.

>>>>

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  The figure shows an initial plan~(in~\ref{sth:i}) re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). 
  Bottom-left shows the energy data of a physical fixed-wing aerial robot flying a static coverage plan similar to the one illustrated here. Bottom-right shows a spectrum analysis of the energy data, revealing the periodicity of the data exploited in the overall energy model.
  %Follow the collected energy data of a physical aerial robot flying the static coverage.
  }
  \label{fig:il-abs}
  \vspace*{-4ex}
\end{figure}

@@

For a set $\mathbb{X}$, $\mathbb{X}_{\geq 0}$ indicates its members are positive, $\mathbb{X}_{> 0}$ strictly positive, and $|\mathbb{X}|$ its cardinality. $\mathbb{Z},\mathbb{R}$ are %the sets of 
integers and reals. % respectively.
Bold letters indicate vectors. 
The notation $[x]$ denotes positive naturals up to $x$, i.e., $\{0,1,\dots,x\}$, $x'$ the transpose of $x$, and $[\underline{x},\overline{x}]$ the upper/lower bounds of a parameter $x$, i.e.,
\begin{equation}
  \underline{x}\leq x\leq\overline{x}.
\end{equation}

@@

\begin{defn}[Triggering and final points]
  \label{def:trigs}
  The \emph{triggering point} $\mathbf{p}_{\Gamma_{i}}$ describes the transition between stages. The \emph{final point} is the last triggering point $\mathbf{p}_{\Gamma_{l}}$ relative to the last stage $\Gamma_l$.
\end{defn}

@@

\begin{defn}[Plan]\label{def:plan}
  The \emph{plan} is a finite state machine (FSM) $\Gamma$, where the state-transition function $s:\bigcup_i{\Gamma_i}\times\mathbb{R}^2\rightarrow\bigcup_i{\Gamma_i}$ maps a stage and a point to the next stage
  \begin{equation*}s(\Gamma_i,\mathbf{p}(t)):=\begin{cases}
    \Gamma_{i+j} & \text{if }\norm{\mathbf{p}(t)-\mathbf{p}_{\Gamma_i}}<\varepsilon_i,\,\exists j\in\mathbb{Z},\\
    \Gamma_i & \text{otherwise}.
  \end{cases}\end{equation*}
\end{defn}

The stage-dependent value $\varepsilon_i\in\mathbb{R}_{\geq 0}$ in Definition~\ref{def:plan} expresses the radius of a non-existent circle over $\mathbf{p}_{\Gamma_i}$.

Fig.~\ref{fig:traj1} illustrates the concepts in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}. $\varphi_0,\dots,\varphi_5$ are path functions. $\varphi_0$ and $\varphi_4$ are circles, while $\varphi_1$, $\varphi_3$, and $\varphi_5$ are lines. They are relative to different stages $\Gamma_1,\dots$ but $\Gamma_0$ (the starting stage) and are changed in the proximity of $\mathbf{p}_{\Gamma_0},\dots$. %The constraint set $\mathcal{C}_{4,1}$ forms the area where 
It is possible to alter the paths $\varphi_1,\dots,\varphi_4$ with the parameters $c_{1,1},\dots,c_{4,1}$ illustrated by the gray area in the figure. %The area relative to $\Gamma_5$ is bounded by $\underline{c}_{5,1}\overline{c}_{5,1}$.

@@

\begin{defn}[Primitive stages]
  \label{def:primitive}
  Given the number of \emph{primitive stages} $n\in\mathbb{Z}_{>0}$, a \emph{shift} $\mathbf{d}\in\mathbb{R}^2$, and a final point $\mathbf{p}_{\Gamma_l}$, the stages $\Gamma_1,\Gamma_2,\dots,\Gamma_n$ %with the path functions $\varphi_1,\dots\varphi_n$ and the parameters $c_1,c_2,\dots,c_n$ 
  are \emph{primitive} if they form the remainder of the plan with $\mathbf{d}$ up to $\mathbf{p}_{\Gamma_l}$. 
\end{defn}
\noindent In this case, the path functions have a constant distance $e_j$ per each value in $[n]_{>0}$, i.e., 
\begin{equation}\label{eq:primitive}\begin{split}
  &\varphi_{(i-1)n+j}(\mathbf{p}+(i-1)\mathbf{d},c_1^\rho)-\varphi_{in+j}(\mathbf{p}+i\mathbf{d},c_1^\rho)=e_j,
\end{split}\end{equation}
holds $\forall i\in[l/n-1]_{>0},j\in[n]_{>0}$ assuming the total number of stages is known and is $l\in\mathbb{Z}_{>0}$. $e_j\in\mathbb{R}$ given a shift $\mathbf{d}$, initial point $\mathbf{p}$, and initial value of path parameters $c_1^\rho$.

@@

Fig.~\ref{fig:state-machine-loop} illustrates  the concepts in Definition~\ref{def:primitive}. A plan composed of $n$ stages $\Gamma_1,\dots,\Gamma_n$ (containing primitive paths $\varphi_1,\dots,\varphi_n$) is reiterated with the shift $\mathbf{d}$. $t_1<\dots<t_4$ are time instants $\in\mathbb{R}_{> 0}$. $\Gamma_f$ is the accepting stage, indicating the plan is complete, $\Gamma_0$ the initial stage where the aerial robot awaits the starting command.

@@

\begin{pb}[Coverage and re-planning-scheduling problem]
  \label{pb:cov-pb}
  Consider a finite set of vertices of a polygon $v:=\{v_1,v_2,\dots\}$ where each %vertex $v_i:=(x_{v_i},y_{v_i})%,\forall i\in[|v|]_{>0}$
  %,\,o_{j,k}:=(x_{o_{j,k}},y_{o_{j,k}}),\,\forall j\in|o|,k\in|o_j|$ 
  is a point w.r.t. $\mathcal{O}_W$. 
  Let $\underline{r}\in\mathbb{R}_{\geq 0}$, the vehicle's turning radius, and $\mathbf{p}(t_0)$, the starting point at the time instant $t_0$, be given. 
  The \emph{coverage problem} is the problem of finding a plan $\Gamma$ to cover the polygon, whereas the \emph{re-planning-scheduling problem} is finding the optimal parameters $c_i$ in time.
\end{pb}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computations parameters on the battery at future time instants. To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies as well as battery evolution.

@@

The collected energy data and corresponding spectrum analysis in Fig.~\ref{fig:il-abs} show the energy of a static coverage plan. It is relative to one flight of a series of flights for CPP exhibiting periodic behavior in a precision agriculture use case~\cite{seewald2020mechanical}. %$\Gamma$ with four primitive path functions iterated with a shift. 
Assuming the primitive paths have approximately the same length and the aerial robot has a fixed ground speed, the data exhibits periodic behavior with a constant set of frequencies, independent of the shift. The hypothesis is further backed by the power spectrum analysis, indicating that to model the energy, three frequencies are adequate.

@@

An intuitive way of modeling the energy data is a Fourier series of a given order $r\in\mathbb{Z}_{\geq 0}$ and period $T\in\mathbb{R}_{>0}$
\begin{equation}\label{eq:fourier}
  h(t)=a_0/T+(2/T)\sum_{j=1}^{r}{\left(a_j\cos{\omega jt}+b_j\sin{\omega jt}\right)},
\end{equation}
where $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ maps time to the instantaneous energy consumption, $\omega:=2\pi/T$ is the angular frequency, and $a,b\in\mathbb{R}$ the series coefficients.

@@

Models for heterogeneous computing hardware in the literature often rely on analytical expressions~\cite{marowka2017energy,goraczko2008energy,calore2015energy,yang2017designing} or different techniques, such as regressional analysis~\cite{bailey2014adaptive,ma2012holistic,seewald2019coarse}, aiding the selection of hardware- or software-specific parameters. This section presents an energy model based on our early studies~\cite{seewald2019component,seewald2019coarse} that relies on regressional analysis to quantify the computations energy of any configuration of computations $c_i^\sigma$ within the bounds (see Definition~\ref{def:stage}).

@@

The energy measures in Definitions~\ref{def:meas}--\hyperref[def:pred]{2} can be either average expressed in watts or overall expressed in joules. Additionally, the \powprof{} tool supports the battery state of charge (SoC) detailed in Section~\ref{sec:mod-bat}. The function $g$ in Definition~\ref{def:pred} is contained in the computations scaling factors in Eq.~(\ref{eq:scale-comp}), assuming the computations energy behaves linearly between $\underline{c}_i^\sigma$ and $\overline{c}_i^\sigma$, otherwise
\begin{equation}\label{eq:piece-wise-reg}\begin{split}
  g(c_i^\sigma)=(&\mathbf{g}(\lceil c_i^\sigma\rceil,\mathcal{T}_1)-\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2))\\(&c_i^\sigma-\lfloor c_i^\sigma\rfloor)/(\lceil c_i^\sigma\rceil-\lfloor c_i^\sigma\rfloor)+\mathbf{g}(\lfloor c_i^\sigma\rfloor,\mathcal{T}_2),
\end{split}\end{equation}
where notation $\lceil c_i^\sigma\rceil,\lfloor c_i^\sigma\rfloor$ indicates two adjacent measurement layers, and $\mathcal{T}_1,\mathcal{T}_2$ are the corresponding two time intervals. The measuring device in both $\mathbf{g}$ and $g$ is implicit.

@@

The battery SoC changes according to~\cite{hasan2018exogenous,zhang2018online}, i.e.,
\begin{equation}\label{eq:batdyn}
  \dot{b}(y(t))=-k_bI(y(t))/Q_c,
\end{equation}
where $I(y(t))\in\mathbb{R}$ is the internal current measured in amperes, $y(t)\in\mathbb{R}_{\geq 0}$ the power drain, and $Q_c\in\mathbb{R}$ the battery constant nominal capacity measured in amperes per hour. $k_b$ is a battery coefficient added to~\cite{hasan2018exogenous,zhang2018online} and derived experimentally. The ``Rint'' circuit models the battery as a perfect voltage source connected with a resistor $R_r\in\mathbb{R}$ measured in ohm, representing the battery resistance. The voltage on the extremes of ECM respects $V_e=V-R_rI$, where $V,V_e\in\mathbb{R}$ are the internal and external battery voltages measured in volts. The former can be retrieved from the battery data sheet~\cite{hinz2019comparison} and depends on the SoC~\cite{hasan2018exogenous}.

@@

This section solves the problem described in Section~\ref{sec:pbfor}. It provides a plan %$\Gamma$ 
and re-plans-schedules such plan energy-wise. %respectively
%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.

@@

There are various approaches in the literature to solve CPP problems (e.g., Section~\ref{sec:pbfor}). Those that ensure the completeness %of the cover 
are NP-hard~\cite{arkin2000approximation} and use cellular decomposition, dividing the free-space into sub-regions to be easily covered~\cite{choset2001coverage,galceran2013survey}.

@@

To implement the variable CPP, the radius $r_2$ of the second circle $\varphi_{|\Gamma|+4}$ on Line~\ref{alg2:circ2}
\begin{equation}\label{eq:r2}
  r_2(c_{i,1}):=\sqrt{r^2+c_{i,1}},
\end{equation}
is expressed as a function of a path parameter $c_{i,1}\in(\underline{r}^2-r^2,0]$, relative to the last circle in each set of primitive stages. $r\in\mathbb{R}_{>0}$ is a given ideal turning radius along with the minimum radius (see Section~\ref{pb:cov-pb}). The center also changes
\begin{equation}\label{eq:second-circ-gene}
  \varphi_{|\Gamma|+4}:=(x-x_{\mathbf{p}_{|\Gamma|+3}}+r_2)^2+(y-y_{\mathbf{p}_{|\Gamma|+3}})^2-r_2^2,
\end{equation}
where $(x_\mathbf{p},y_\mathbf{p})=:\mathbf{p}$ for any point $\mathbf{p}$. Fig.~\ref{fig:tee1} illustrates the concept of $c_{i,1}$ altering the CPP. The radius of the first circle on Line~\ref{alg2:circ1} is then $r_1:=r+x_\mathbf{d}/2$ (i.e., the radiuses of the two circles ensure that the primitive paths are shifted of $\mathbf{d}$).% in Definition~\ref{def:primitive}).

@@

\begin{figure*}
  \centering
  \begin{subfigure}{.4\textwidth}
    \centering
    \footnotesize
    \input{\figpath/results/new_physics2/trajs3.tikz}
    \caption{Path, parameters ($c_{i,1},c_{i,2}$) evolutions}
    \label{fig:trajs}
  \end{subfigure}\hspace*{3ex}
  \begin{subfigure}{.54\textwidth}
    \centering
    \footnotesize
    \input{\figpath/results/new_physics2/ener3.tikz}
    \caption{Energies, model states ($\alpha_0,\dots\in\mathbf{q}$), and parameters ($T,b_0$) evolutions}
    \label{fig:ener}
  \end{subfigure}
  \footnotesize
  \caption{CPP with novel Zamboni-like motion (\hyperref[fig:trajs-I-static]{I},\hyperref[fig:trajs-II-static]{II}) and Planning-scheduling of CPP and ground patterns detections with PedNet CNN (\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-dyn-ii]{ii}) in terms of the path, energies, and plans-schedules under different conditions (\hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i},\hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii}): wind speed and direction, battery behavior, and parameters initial values.}
  \label{fig:res}
  \vspace*{-3ex}
\end{figure*}

\vspace*{-1.5ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Simulations} %
\label{sec:experimental}        %
                                %
%$\subsection{Experimental setup}

Numerical simulations of Algorithms~\ref{alg2}--\ref{alg} in this section are implemented in \textsc{Matlab}\hspace{.5ex}(R), and are extended with the computations energy model on NVIDIA\hspace{.5ex}(R) Jetson Nano\hspace{.5ex}(TM) heterogeneous computing hardware. These simulations complement early data of physical flights of a static coverage plan with the open-source Paparazzi flight controller~\cite{papa}.
The computing hardware carries a camera as a peripheral and is evaluated independently of the aerial robot with \powprof{} (see Section~\ref{sec:mod-com}). The scheduler, implemented using the Robot Operating System (ROS) middleware~\cite{quigley2009ros}, varies a computation parameter $c_{i,2}$ relative to the ground patterns detection rate from two to ten frames per second (FPS). The detection uses PedNet, a Convolutional Neural Network (CNN)~\cite{ullah2018pednet}, also implemented using ROS. The planner varies the path parameter $c_{i,1}$ in Eq.~(\ref{eq:r2}) between zero and -1000 (i.e., the planner-scheduler is the concrete implementation of Algorithms~\ref{alg2}--\ref{alg}). The set of parameters is unaltered through the flight, i.e, $c_i:=\begin{bmatrix}c_{i,1}&c_{i,2}\end{bmatrix}',\forall i$.

%The algorithm that we presented in this paper is motivated by a periodic behavior of empirical data on energy consumption (see the subfigures of Fig.~\ref{fig:il-abs}). 
Fig.~\ref{fig:il-abs} details the data of the physical flight  
%We collected these data flying Opterra, a fixed-wing UAV that we adapted for an agricultural scenario. The UAV was flying 
in standard atmospheric conditions. 
Fig.~\ref{fig:res} extends the flight with the computing hardware aided by a flight simulation implemented in \textsc{Matlab}\hspace{.5ex}(R). 
Upper-case roman numerals I,II indicate the plans are static (i.e., solely Algorithm~\ref{alg2}), lower-case i,ii exploit planning-scheduling as described in this letter.

@@

\vspace*{-1.5ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Directions}  %
\label{sec:conclusion}                       %
                                             %
This letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature. It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings. Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool. The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC. It evolves the state of the energy model while optimizing battery usage and remedying possible defects. The plan compromise multiple stages, where at each stage the aerial robot flies a path and runs the computations, allowing %further 
extensibility in terms of constructs and approaches.

Indeed, we are currently extending the results to a standard flight controller to enable physical experiments. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
and distributed planning-scheduling merit additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots. Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.
Further future directions include the study of different energy models. Amongst others, these include aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models.% In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.
